VISUALIZATION OF THE RIEMANN-LIOUVILLE FRACTIONAL INTEGRAL \\ [3pt] IN ``FCAA'' JOURNAL

### 2019-10-16 fractional/FCAA/Authors Kit (Updated)/FCAA-template-for-authors.tex
added some new sections to article

Consider the Riemann-Stieltjes integral $\int_{a'}^{b'} f(x)\,\widetilde{g}(x)$. Assume that $\widetilde{g}(x)$ is a differentiable and invertable real-valued function on $[a',b']$. Moreover, recall that 
\begin{equation}
\label{eq:g_def2}
g(x) = x - a\circ f(x) + a.
\end{equation}
Let $g(x) = \widetilde{g}(x) + C$. Assume that the real-valued constants $C$ and $a$ are unknown. Furthermore, note that (see Theorem xx):
\begin{equation}
\int_{a'}^{b'} f(x)\,dg(x) = \int_{a'}^{b'}f(x)\,\widetilde{g}(x), 
\end{equation}
At first, it seems impossible to compute $a(y)$ given $\widetilde{g}(x)$ as $C$ and $a$ are unknown a priori. However, 
\begin{equation}
\label{eq:implies}
g(a') = \widetilde{g}(a') + C \implies C = a - \widetilde{g}(a'). 
\end{equation}
Substituting Equation~\eqref{eq:implies} into Equation~\eqref{eq:g_def2} eliminates
both $a$ and $C$ from it. If we then solve for $a(y)$ we obtain:
\begin{equation}
a(y) = f^{-1}(y)-\widetilde{g}\circ f^{-1}(y) + \widetilde{g}(a'). 
\end{equation}
We can now compute the following:
\begin{itemize}
\item Compute $a = a(0)$.
\item Compute $C = a - \widetilde{g}(a')$.
\item Compute $g(x) = \widetilde{g}(x) + C$.
\item Compute $h(x) = g^{-1}(x)$.
\item Compute $b = g(b')$ and $b(y) = a(y) + (b-a)$.
\end{itemize}
It now follows that 
\begin{equation}
\int_{a'}^{b'} f(x)d\,\widetilde{g}(x) = \int_{a'}^{b'} f(x)d\,g(x):=\int_{a(y)}^{b(y)}f(x)dx. 
\end{equation}
The above derivation implies that not every Riemann-Stieltjes integral can be converted into a Cavalieri integral. It, however, does tell us that every Riemann-Stieltjes integral can be converted into an equivalent Riemann-Stieltjes integral, which in turn, can be converted into a Cavalieri integral. The latter Riemann-Stieltjes integral is obtained by computing the constant $C$. These concepts are clarified in Section~\ref{} via a worked out example.

>>>>

Consider the Riemann-Stieltjes integral $\int_{a'}^{b'} f(x)\,\widetilde{g}(x)$. Assume that $\widetilde{g}(x)$ is a differentiable and invertable real-valued function on $[a',b']$. Assume that the real-valued constants $C$ and $a$ are unknown. Assume further that $C$ is chosen so that the following expression is true:
\begin{equation}
g(x) := \widetilde{g}(x)+C, 
\end{equation}
where  
\begin{equation}
\label{eq:g_def2}
g(x) = x - a\circ f(x) + a.
\end{equation}
Assume that the real-valued constant $a$ is unknown Furthermore, note that (see Theorem xx):
\begin{equation}
\int_{a'}^{b'} f(x)\,dg(x) = \int_{a'}^{b'}f(x)\,\widetilde{g}(x), 
\end{equation}
with $g(x) = \widetilde{g}(x)+C$. 
At first, it seems impossible to compute $a(y)$ given $\widetilde{g}(x)$ as $C$ and $a$ are unknown a priori. However, 
\begin{equation}
\label{eq:implies}
g(a') = \widetilde{g}(a') + C \implies C = a - \widetilde{g}(a'). 
\end{equation}
Substituting Equation~\eqref{eq:implies} into Equation~\eqref{eq:g_def2} eliminates
both $a$ and $C$ from it. If we then solve for $a(y)$ we obtain:
\begin{equation}
a(y) = f^{-1}(y)-\widetilde{g}\circ f^{-1}(y) + \widetilde{g}(a'). 
\end{equation}
We can now compute the following:
\begin{itemize}
\item Compute $a = a(0)$.
\item Compute $C = a - \widetilde{g}(a')$.
\item Compute $g(x) = \widetilde{g}(x) + C$.
\item Compute $h(x) = g^{-1}(x)$.
\item Compute $b = g(b')$ and $b(y) = a(y) + (b-a)$.
\end{itemize}
It now follows that 
\begin{equation}
\int_{a'}^{b'} f(x)d\,\widetilde{g}(x) = \int_{a'}^{b'} f(x)d\,g(x):=\int_{a(y)}^{b(y)}f(x)dx. 
\end{equation}
The above derivation implies that not every Riemann-Stieltjes integral can be converted into a Cavalieri integral. It, however, does tell us that every Riemann-Stieltjes integral can be converted into an equivalent Riemann-Stieltjes integral, which in turn, can be converted into a Cavalieri integral. The latter Riemann-Stieltjes integral is obtained by computing the constant $C$. These concepts are clarified in Section~\ref{} via a worked out example.
